Normalized expressions

### 2021-04-09 analysis/environments.Rmd

eval_calls_explicit <- E_envir %>% filter(is.na(envir))
nb_explicit <- count(eval_calls_explicit, wt = duplicates)
nb_explicit_sites <- nb_eval_call_sites(eval_calls_explicit)

@@

```{r envir_absolute}
eval_calls_absolute <- eval_calls_explicit %>%
  anti_join(eval_calls_env_list) #%>%
  #anti_join(eval_calls_arg_caller)

@@

nb_global_env_sites <- specific_env %>% filter(specific_env == "global") %>% .$n
nb_callee_env_sites <- specific_env %>% filter(specific_env == "callee") %>% .$n
if(length(nb_callee_env_sites) == 0) nb_callee_env_sites <- 0
nb_empty_env_sites <- specific_env %>% filter(specific_env == "empty") %>% .$n
if(length(nb_empty_env_sites) == 0) nb_empty_env_sites <- 0
nb_base_env_sites <- specific_env %>% filter(specific_env == "base") %>% .$n
if(length(nb_base_env_sites) == 0) nb_base_env_sites <- 0

@@

```{r}
env_calls <- env_calls %>%
  mutate(env_class = if_else(environment_class == "loop", "loop", paste0(if_else(is.na(hierarchy), specific_env, as.character(hierarchy)), if_else(is.na(new_env), "", "+"))))
```

@@

>>>>

eval_calls_explicit <- E_envir %>% filter(!is.na(envir))
nb_explicit <- count(eval_calls_explicit, wt = duplicates)
nb_explicit_sites <- nb_eval_call_sites(eval_calls_explicit)

@@

```{r envir_absolute}
eval_calls_absolute <- eval_calls_explicit %>% filter(envir_type == "environment")

@@

nb_global_env_sites <- specific_env %>% filter(specific_env == "global") %>% .$n
nb_callee_env_sites <- specific_env %>% filter(specific_env == "callee") %>% .$n # Seems it is actually for envir == "new.env()"
if(length(nb_callee_env_sites) == 0) nb_callee_env_sites <- 0
nb_empty_env_sites <- specific_env %>% filter(specific_env == "empty") %>% .$n
if(length(nb_empty_env_sites) == 0) nb_empty_env_sites <- 0
nb_base_env_sites <- specific_env %>% filter(specific_env == "base") %>% .$n
if(length(nb_base_env_sites) == 0) nb_base_env_sites <- 0

@@

@@

TODO: if there is both new , a caller-n, a specific class, rather ignore the caller-n
```{r}
env_classes <- env_calls %>%
  mutate(env_class = if_else(environment_class == "loop", "loop", paste0(if_else(is.na(hierarchy), specific_env, as.character(hierarchy)), if_else(is.na(new_env), "", "+"))))

env_classes %>% count(env_class, wt = duplicates, sort = TRUE) %>%
  mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc)) %>%
  datatable()

env_classes %>% group_by(env_class) %>% summarise(n = n_distinct(src_ref)) %>%
  arrange(desc(n)) %>%
  mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc)) %>%
  datatable()
```

# Specific envir with their environment class

For the default argument:

```{r}
eval_calls_default %>% count(environment_class, wt = duplicates, sort = TRUE) %>%
  mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc))

eval_calls_default %>% group_by(environment_class) %>% summarise(n = n_distinct(src_ref)) %>%
  arrange(desc(n)) %>%
   mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc))

# caller-2- is eval.parent
eval_calls_default %>% filter(environment_class == "caller-2-") %>% count(ev_variant)

`eval` is not problematic:

```{r}
eval_calls_default %>% filter(ev_variant == "eval") %>% count(environment_class, wt = duplicates, sort = TRUE)
```

But `eval.parent` is:

```{r}
eval_calls_default %>% filter(ev_variant == "eval.parent") %>% count(environment_class, wt = duplicates, sort = TRUE)
```

It might be because `parent.frame` is equivalent to  `sys.frame(sys.parent(n))` and `sys.parent(n)` can get surprising result of it is called near the top level...

For `parent.frame()` :

```{r}
E_envir %>% filter(envir == "parent.frame()") %>% count(environment_class, wt = duplicates, sort = TRUE) %>%
  mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc))

E_envir %>% filter(envir == "parent.frame()") %>% group_by(environment_class) %>%
  summarise(n = n_distinct(src_ref)) %>%
  arrange(desc(n)) %>%
   mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc))

For `new.env()`:

```{r}
E_envir %>% filter(envir == "new.env()") %>% count(environment_class, wt = duplicates, sort = TRUE) %>%
  mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc))

E_envir %>% filter(envir == "new.env()") %>% group_by(environment_class) %>%
  summarise(n = n_distinct(src_ref)) %>%
  arrange(desc(n)) %>%
   mutate(pc = round(100 * n / sum(n), 2), cpc = cumsum(pc))

For each envir expression, what is the most common environment class? (in calls, in sites)

```{r}
env_class_envir <- E_envir %>% group_by(envir) %>%
  group_by(environment_class, .add = TRUE) %>% summarise(n = n_distinct(src_ref)) %>%
  summarise(env_class = first(environment_class, order_by = order(n, decreasing = TRUE)), n = sum(n)) %>% 
  arrange(desc(n))
```

### 2021-04-09 analysis/normalized.Rmd

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), 
            proportion = ratio(n_call_sites, nb_call_sites), 
            n_packages = n_distinct(ev_package),
            n_operations = round(mean(n_op, na.rm=TRUE), 2), 
            med_operations = median(n_op, na.rm = TRUE),
            percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), 
            percent_envir_calls = ratio(sum(!is.na(envir)), n()), 
            env_diversity = n_distinct(envir), 
            percent_envir_non_parentframe = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir) & cur_data()$envir != "parent.frame()"]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

@@

```{r}
nrows <- min(12, nrow(widespread_minimized)) # kaggle has less than 12 rows
r_vec("MinimizedCallSites", nrows, pull(widespread_minimized, n_call_sites))
r_vec("MinimizedPropSites", nrows, pull(widespread_minimized, proportion))
r_vec("MinimizedPackage", nrows, pull(widespread_minimized, n_packages))
r_vec("MinimizedOperations", nrows, pull(widespread_minimized, n_operations))
r_vec("MinimizedPercentEnvir", nrows, pull(widespread_minimized, percent_envir))
r_vec("MinimizedPercentEnvirNonParent", nrows, pull(widespread_minimized, percent_envir_non_parentframe))
```

>>>>

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), 
            proportion = ratio(n_call_sites, nb_call_sites), 
            n_packages = n_distinct(ev_package),
            n_operations = round(mean(n_op, na.rm=TRUE)), 
            med_operations = median(n_op, na.rm = TRUE),
            percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), 
            percent_envir_calls = ratio(sum(!is.na(envir)), n()), 
            env_diversity = n_distinct(envir), 
            percent_envir_non_parentframe = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir) & cur_data()$envir != "parent.frame()"]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

@@

```{r}
nrows <- min(12, nrow(widespread_minimized)) # kaggle has less than 12 rows
r_vec("MinimizedCallSites", nrows, pull(widespread_minimized, n_call_sites))
r_vec("MinimizedPropSites", nrows, pull(widespread_minimized, proportion), digits=0)
r_vec("MinimizedPackage", nrows, pull(widespread_minimized, n_packages))
r_vec("MinimizedOperations", nrows, pull(widespread_minimized, n_operations))
r_vec("MinimizedMedianOperations", nrows, pull(widespread_minimized, med_operations))
r_vec("MinimizedPercentEnvir", nrows, pull(widespread_minimized, percent_envir), digits=0)
r_vec("MinimizedPercentEnvirNonParent", nrows, pull(widespread_minimized, percent_envir_non_parentframe), digits=0)
```
